Planetary perturbers: Flaring star-planet interactions in Kepler and TESS

### 2023-10-06 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{table*}
    \script{paper_latex_flare_table.py}
    \centering
            \caption{
            Flare catalog of all star-planet systems observed by Kepler and TESS (as of July 2022). In transiting multi-planet systems, the orbital phase refers to the innermost planet, with the transit mid-time at phase zero. The full catalog is available online (see Data Availability Statement).
        }
    \input{output/flare_table.tex}
        \label{tab:flares}
\end{table*}

>>>>

\begin{table*}
    \script{paper_latex_flare_table.py}
    \centering
            \caption{
            Flare catalog of all star-planet systems observed by Kepler and TESS (as of July 2022). In transiting multi-planet systems, the orbital phase refers to the innermost planet, with the transit mid-time at phase zero. \textcolor{red}{Qua./Sec. is the Quarter or Sector number of the observation in Kepler or TESS, respectively. The first and last data point of the flare are denoted $t_s$ and $t_f$. The orbital phase of the innermost planet is measured at $t_s$. Relative amplitude $a$, and equivalent duration $ED$ (see Eq.~\ref{eq:ED}) are given for each flare.} The full catalog is available online (see Data Availability Statement).
        }
    \input{output/flare_table.tex}
        \label{tab:flares}
\end{table*}
